### 2016-06-24 templates/report/scientific_mission/tex/scientific_missions.tex
NIRA-107 - Change scientific mission to register multiple routes

{% autoescape off %}{% block content %}\begin{longtable}{ |p{4cm}|p{5,4cm}|p{2cm}|p{1,8cm}|p{1,8cm}| }
\hline
Researcher & Scientific mission & Local & Start date & End date \\ \hline
{% for mission in missions %}{% if mission.person and mission.person.institution == None %}{{ mission.person }}{% elif mission.person and mission.person.institution != None %}{{ mission.person }} / {{ mission.person.institution.get_person_institution }}{% endif %} &{% if mission.mission != None and mission.project_activity != None %}{{ mission.mission }}{{ mission.project_activity.title }}{% elif mission.mission != None %}{{ mission.mission }}{% elif mission.project_activity != None %}{{ mission.project_activity.title }}{% else %}No scientific missions found!{% endif %} &{{ mission.destination_city }} &  {{ mission.departure|date:"M d, Y" }} & {{ mission.arrival|date:"M d, Y" }}\\ \hline {% endfor %}
\end{longtable}

{% endblock %}
{% endautoescape %}

>>>>

{% autoescape off %}{% block content %}\begin{longtable}{ |p{4cm}|p{5,4cm}|p{2cm}|p{1,8cm}|p{1,8cm}| }
\hline
Researcher & Scientific mission & Local & Start date & End date \\ \hline
{% for item in missions %}{% if item.mission.person and item.mission.person.institution == None %}{{ item.mission.person }}{% elif item.mission.person and item.mission.person.institution != None %}{{ item.mission.person }} / {{ item.mission.person.institution.get_person_institution }}{% endif %} & {% if item.mission.mission != None and item.mission.project_activity != None %}{{ item.mission.mission }}{{ item.mission.project_activity.title }}{% elif item.mission.mission != None %}{{ item.mission.mission }}{% elif item.mission.project_activity != None %}{{ item.mission.project_activity.title }}{% else %}No scientific missions found!{% endif %} & {% if item.mission.destination_city.country.name == 'Brazil' %}{{ item.mission.destination_city.name }} - {{ item.mission.destination_city.region.alternate_names }}{% else %}{{ item.mission.destination_city.name }}, {{ item.mission.destination_city.country }}{% endif %} &  {{ item.departure.departure|date:"M d, Y" }} & {{ item.arrival.departure|date:"M d, Y" }}\\ \hline {% endfor %}
\end{longtable}{% endblock %}{% endautoescape %}
